### 2025-06-21 download-football-data.qmd
20250621 - variable names

# Downloaded Data - Raw
load(file = "./data/nfl_players_raw.RData")
load(file = "./data/nfl_teams_raw.RData")
load(file = "./data/nfl_rosters_raw.RData")
load(file = "./data/nfl_rosters_weekly_raw.RData")
load(file = "./data/nfl_schedules_raw.RData")
load(file = "./data/nfl_combine_raw.RData")
load(file = "./data/nfl_draftPicks_raw.RData")
load(file = "./data/nfl_depthCharts_raw.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_4thdown_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation_raw.RData", fsep = ""))
load(file = "./data/nfl_actualStats_position_weekly_raw.RData")
load(file = "./data/nfl_actualStats_weekly_raw.RData")
load(file = "./data/nfl_injuries_raw.RData")
load(file = "./data/nfl_snapCounts_raw.RData")
load(file = "./data/nfl_espnQBR_seasonal_raw.RData")
load(file = "./data/nfl_espnQBR_weekly_raw.RData")
load(file = "./data/nfl_nextGenStats_weekly_raw.RData")
load(file = "./data/nfl_advancedStatsPFR_seasonal_raw.RData")
load(file = "./data/nfl_advancedStatsPFR_weekly_raw.RData")
load(file = "./data/nfl_playerContracts_raw.RData")
load(file = "./data/nfl_ftnCharting_raw.RData")
load(file = "./data/nfl_playerIDs_raw.RData")
load(file = "./data/nfl_rankings_draft_raw.RData")
load(file = "./data/nfl_rankings_weekly_raw.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_weekly_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_pbp_raw.RData", fsep = ""))
load(file = "./data/players_projections_seasonal_raw.RData")

@@

# Downloaded Data - Processed
load(file = "./data/nfl_players.RData")
load(file = "./data/nfl_teams.RData")
load(file = "./data/nfl_rosters.RData")
load(file = "./data/nfl_rosters_weekly.RData")
load(file = "./data/nfl_schedules.RData")
load(file = "./data/nfl_combine.RData")
load(file = "./data/nfl_draftPicks.RData")
load(file = "./data/nfl_depthCharts.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_4thdown.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation.RData", fsep = ""))
load(file = "./data/nfl_actualStats_position_weekly.RData")
load(file = "./data/nfl_actualStats_weekly.RData")
load(file = "./data/nfl_injuries.RData")
load(file = "./data/nfl_snapCounts.RData")
load(file = "./data/nfl_espnQBR_seasonal.RData")
load(file = "./data/nfl_espnQBR_weekly.RData")
load(file = "./data/nfl_nextGenStats_weekly.RData")
load(file = "./data/nfl_advancedStatsPFR_seasonal.RData")
load(file = "./data/nfl_advancedStatsPFR_weekly.RData")
load(file = "./data/nfl_playerContracts.RData")
load(file = "./data/nfl_ftnCharting.RData")
load(file = "./data/nfl_playerIDs.RData")
load(file = "./data/nfl_rankings_draft.RData")
load(file = "./data/nfl_rankings_weekly.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_pbp.RData", fsep = ""))
load(file = "./data/players_projectedPoints_seasonal.RData")

# Calculated Data - Processed
load(file = "./data/nfl_actualStats_career.RData")
load(file = "./data/nfl_actualStats_seasonal.RData")
load(file = "./data/nfl_actualFantasyPoints_career.RData")
load(file = "./data/nfl_actualFantasyPoints_seasonal.RData")
load(file = "./data/nfl_actualFantasyPoints_weekly.RData")
```

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

# Downloaded Data - Raw
load(file = "./data/nfl_players_raw.RData")
load(file = "./data/nfl_teams_raw.RData")
load(file = "./data/nfl_rosters_raw.RData")
load(file = "./data/nfl_rosters_weekly_raw.RData")
load(file = "./data/nfl_schedules_raw.RData")
load(file = "./data/nfl_standings_raw.RData")
load(file = "./data/nfl_combine_raw.RData")
load(file = "./data/nfl_draftPicks_raw.RData")
load(file = "./data/nfl_draftValues_raw.RData")
load(file = "./data/nfl_depthCharts_raw.RData")
load(file = "./data/nfl_trades_raw.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_4thdown_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation_raw.RData", fsep = ""))
load(file = "./data/nfl_actualStats_position_weekly_raw.RData")
load(file = "./data/nfl_actualStats_weekly_raw.RData")
load(file = "./data/nfl_injuries_raw.RData")
load(file = "./data/nfl_snapCounts_raw.RData")
load(file = "./data/nfl_espnQBR_seasonal_raw.RData")
load(file = "./data/nfl_espnQBR_weekly_raw.RData")
load(file = "./data/nfl_nextGenStats_weekly_raw.RData")
load(file = "./data/nfl_advancedStatsPFR_seasonal_raw.RData")
load(file = "./data/nfl_advancedStatsPFR_weekly_raw.RData")
load(file = "./data/nfl_playerContracts_raw.RData")
load(file = "./data/nfl_ftnCharting_raw.RData")
load(file = "./data/nfl_playerIDs_raw.RData")
load(file = "./data/nfl_rankings_draft_raw.RData")
load(file = "./data/nfl_rankings_weekly_raw.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_weekly_raw.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_pbp_raw.RData", fsep = ""))
load(file = "./data/players_projections_seasonal_raw.RData")
load(file = "./data/players_projections_weekly_raw.RData")

@@

# Downloaded Data - Processed
load(file = "./data/nfl_players.RData")
load(file = "./data/nfl_teams.RData")
load(file = "./data/nfl_rosters.RData")
load(file = "./data/nfl_rosters_weekly.RData")
load(file = "./data/nfl_schedules.RData")
load(file = "./data/nfl_standings.RData")
load(file = "./data/nfl_combine.RData")
load(file = "./data/nfl_draftPicks.RData")
load(file = "./data/nfl_draftValues.RData")
load(file = "./data/nfl_depthCharts.RData")
load(file = "./data/nfl_trades.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_4thdown.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation.RData", fsep = ""))
load(file = "./data/nfl_actualStats_position_weekly.RData")
load(file = "./data/nfl_actualStats_weekly.RData")
load(file = "./data/nfl_injuries.RData")
load(file = "./data/nfl_snapCounts.RData")
load(file = "./data/nfl_espnQBR_seasonal.RData")
load(file = "./data/nfl_espnQBR_weekly.RData")
load(file = "./data/nfl_nextGenStats_weekly.RData")
load(file = "./data/nfl_advancedStatsPFR_seasonal.RData")
load(file = "./data/nfl_advancedStatsPFR_weekly.RData")
load(file = "./data/nfl_playerContracts.RData")
load(file = "./data/nfl_ftnCharting.RData")
load(file = "./data/nfl_playerIDs.RData")
load(file = "./data/nfl_rankings_draft.RData")
load(file = "./data/nfl_rankings_weekly.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_expectedFantasyPoints_pbp.RData", fsep = ""))
load(file = "./data/players_projectedPoints_seasonal.RData")
load(file = "./data/players_projectedPoints_weekly.RData")

# Calculated Data - Processed
load(file = "./data/nfl_actualStats_career.RData")
load(file = "./data/nfl_actualStats_seasonal.RData")
load(file = "./data/nfl_actualFantasyPoints_career.RData")
load(file = "./data/nfl_actualFantasyPoints_seasonal.RData")
load(file = "./data/nfl_actualFantasyPoints_weekly.RData")
load(file = "./data/player_stats_weekly.RData")
load(file = "./data/player_stats_seasonal.RData")
```

@@

Here are the variable names:

```{r}
names(nfl_players) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_teams) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_playerIDs) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_rosters) %>% as.data.frame()

names(nfl_rosters_weekly) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_schedules) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_standings) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_combine) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_draftPicks) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_draftValues) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_depthCharts) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_trades) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_pbp) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_4thdown) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_participation) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_actualStats_offense_weekly) %>% as.data.frame()

names(nfl_actualStats_defense_weekly) %>% as.data.frame()

names(nfl_actualStats_kicking_weekly) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_injuries) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_snapCounts) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_espnQBR_seasonal) %>% as.data.frame()

names(nfl_espnQBR_weekly) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_nextGenStats_weekly) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_advancedStatsPFR_seasonal) %>% as.data.frame()

names(nfl_advancedStatsPFR_weekly) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_playerContracts) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_ftnCharting) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_rankings_weekly) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_expectedFantasyPoints_pbp) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(dplyr::bind_rows(players_projectedPoints_seasonal)) %>% as.data.frame()

names(players_projections_seasonal_average) %>% as.data.frame()

names(dplyr::bind_rows(players_projectedPoints_weekly)) %>% as.data.frame()

names(players_projections_weekly_average) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_actualStats_seasonal_player) %>% as.data.frame()

names(nfl_actualStats_seasonal_team) %>% as.data.frame()

names(nfl_actualStats_seasonal_player_inclPost) %>% as.data.frame()

names(nfl_actualStats_seasonal_team_inclPost) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_actualStats_career_player) %>% as.data.frame()

names(nfl_actualStats_career_player_inclPost) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_actualStats_weekly_player) %>% as.data.frame()

names(nfl_actualStats_weekly_team) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_actualFantasyPoints_player_weekly) %>% as.data.frame()

names(nfl_actualFantasyPoints_dst_weekly) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_actualFantasyPoints_player_seasonal) %>% as.data.frame()

names(nfl_actualFantasyPoints_dst_seasonal) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(nfl_actualFantasyPoints_player_career) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(player_stats_weekly) %>% as.data.frame()
```

@@

Here are the variable names:

```{r}
names(player_stats_seasonal) %>% as.data.frame()
```
